{\fontfamily{ptm}\selectfont Linear Convergence of Accelerated Gradient without Restart}

### 2025-08-14 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
>w<, nontrivial changes

\title{{\fontfamily{ptm}\selectfont My Ideas after Reading Necoara's Papers}}

@@

\maketitle
\todoinline{This paper is currently in draft mode. Check source to change options. }
% \vskip 8mm

\begin{abstract} 
    \noindent
    This is still a note for a draft so no abstract \cite{bauschke_convex_2017}
\end{abstract}

@@

% ==============================================================================
\section{Introduction}
    Necoara et al. \cite{necoara_linear_2019}  introduced the definition of quasi strongly convex function (Q-SCNVX), Quadratic Under approximations (QUA), Quadratic Gradient Growth (QGG), Proximal Error Bound (PEB) and, Quadratic Function Growth (QFG). 
    These conditions are relaxation of strong convexity which enables linear convergence rate of first order method, including Nesterov's accelerated variants. 
    In this file, we showed a new perspective of their works. 
    Our goal is to relax their definitions and, to extend the linear convergence results, using completely new ideas and perspective. 
    \par
    \textbf{Notations.}
    Unless specified, our ambient space is $\RR^n$ with Euclidean norm $\Vert \cdot\Vert$.
    Let $C\subseteq \RR^n$, $\Pi_C(\cdot)$ denotes the projection onto the set $C$, i.e: the closest point in $C$ to another point in $\RR^n$. 
    \par
    The following definitions and assumptions are their. 
    % SYMBOL SET FOR THIS CHAPTER ONLY!

    \begin{assumption}[Necoara's linear convergence assumptions]\; \label{ass:necoara-linear} \\
        The following assumptions are about $(f, X, X^*, L_f)$. 
        \begin{enumerate}[nosep]
            \item $f: \RR^n \rightarrow \RR$ is an $L_f$ Lipschitz smooth function. 
            \item $X \subseteq \RR^n$ is a closed convex non-empty set. 
            \item $X^* = \argmin_{x \in X} f(x) \neq \emptyset$. 
        \end{enumerate}
    \end{assumption}
    Under this assumption, the following definitions are proposed. 
    \newcommand{\QSCNVX}{\ensuremath{q\mathcal{S}}}
    \newcommand{\QUA}{\ensuremath{\mathcal U}}
    \newcommand{\QGG}{\ensuremath{\mathcal G}}
    \newcommand{\QFG}{\ensuremath{\mathcal F}} 
    \newcommand{\PEB}{\ensuremath{\mathcal E}}
    \begin{definition}[Necoara's weaker characterizations of strong convexity]\; \\
        Suppose that $(f, X, X^*, L_f)$ are given by Assumption \ref{ass:necoara-linear}. 
        For all $x \in X$, denote $\bar x = \Pi_{X^*}x$. 
        The following definitions are relaxations of strong convexity. 
        \begin{enumerate}[nosep]
            \item $f$ is Q-SCNVX if there exists $\kappa_f > 0$ such that $f(\bar x) - f(x) - \langle \nabla f(x), \bar x - x\rangle \ge \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2$. 
            Which we denote it by $f \in \QSCNVX(f, L_f, \kappa_f)$. 
            \item $f$ is QUA if there exists $\kappa_f > 0$ such that $f(x) - f(\bar x) - \langle \nabla f(\bar x), x - \bar x\rangle \ge \frac{\kappa_f}{2}\Vert x -\bar x\Vert^2$. 
            We denote it by $f \in \QUA(f, L_f, \kappa_f)$.
            \item $f$ is QGG if there exists $\kappa_f > 0$ such that $\langle \nabla f(x) - \nabla f(\bar x), x - \bar x\rangle \ge \frac{\kappa}{2}\Vert x - \bar x\Vert^2$. 
            We denote it by $f \in \QGG(f, L_f, \kappa_f)$. 
            \item $f$ is PEB if there exists $\kappa_f > 0$ such that $\left\Vert x - L^{-1}\Pi_X(x - L^{-1}\nabla f(x))\right\Vert \ge \kappa_f\Vert x - \bar x\Vert$. 
            We denote it by $f \in \PEB(f, L_f, \kappa_f)$. 
            \item $f$ is QFG if there exists $\kappa_f > 0$ such that $f(x) - f(\bar x) \ge \frac{\kappa_f}{2}\Vert x - \bar x\Vert^2$. 
            We denote it by $f \in \QFG(f, L_f, \kappa_f)$. 
        \end{enumerate}
    \end{definition}
    These definitions are the keys which Necoara used to prove the linear convergence of projected gradient, and Nesterov's accelerated gradient method.

\section{Precurors materials for our proofs of linear convergence}
    We propose an alternative approach that extends the results, and make comparison with existing works from Necoara et al.

\section{Linear convergence of first order methods}

>>>>

\title{{\fontfamily{ptm}\selectfont Linear Convergence of Accelerated Gradient without Restart}}

@@

\maketitle
\todoinline{This paper is currently in draft mode. Check source to change options. \cite{bauschke_convex_2017}}
% \vskip 8mm

\begin{abstract} 
    \noindent
    This is still a note for a draft so no abstract. 
\end{abstract}

@@

% ==============================================================================
\section{Introduction}
    \textbf{Notations.}
    Unless specified, our ambient space is $\RR^n$ with Euclidean norm $\Vert \cdot\Vert$.
    Let $C\subseteq \RR^n$, $\Pi_C(\cdot)$ denotes the projection onto the set $C$, i.e: the closest point in $C$ to another point in $\RR^n$. 
    For a function of $F = f + g$, and a $B\ge 0$ where $f$ is $\mathcal C^1$ differentiable, and $g$ is l.s.c, we consider the proximal gradient operator: 
    \begin{align*}
        T_B(x) &= \argmin_{z} \left\lbrace
            g(z) + f(x) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert x - z\Vert^2
        \right\rbrace
        \\
        &= \hprox_{B^{-1}g}(x - B^{-1}\nabla f(x)). 
    \end{align*}
    We also define the gradient mapping operator

\section{Precursors materials for our proofs of linear convergence}
    \begin{definition}[similar triangle form of accelerated proximal gradient]\label{def:st-apg}

    \end{definition}

\section{deriving the convergence rate}
    \subsection{preparations}
        \begin{lemma}[convergence preparations part I]

        \end{lemma}
        \begin{lemma}[convergence preparations part II]

        \end{lemma}
        \begin{lemma}[convergence preparations part III]

        \end{lemma}
